An eight-year-long low-frequency earthquake catalog for Southern Cascadia

### 2022-01-26 paper/answer_reviewers.tex

\bigskip

\textit{Line 138: Why did authors used such a long (1 min) time window for matched filter analysis. I think it is common to use time windows of 5 - 10 seconds around the arrival time at each seismic station (e.g., Shelly et al., 2007, https://doi.org/10.1038/nature05666; Kato and Nakagawa, 2020, https://doi.org/10.1186/s40623-020-01257-4).}

\bigskip

The templates from Plourde et al. (2015) have a low signal-to-noise ratio and generally do not show clear P- and S-wave arrivals, so the 60 seconds window helps be sure it contains the P and S waves. Moreover, the wave arrivals can be located close to the beginning or close to the end of the time window, depending on the LFE family considered. We have chosen to keep the whole one-minute time window to be sure to include both the P- and the S-wave arrivals. The templates obtained using LFE detections from the 2-year-long catalog show clearer P- and S-wave arrivals and we have reduced the length of the time window to 30 seconds on average, depending on the LFE family considered. We have remade the templates using only LFEs that were present in both catalogs (FAME and permanent networks). The wave arrivals are now clearer and, to extend farther in time our catalog, we could reduce the size of the time window by using a different starting time for each station, depending on whether it is close or farther away from the LFE source location.

@@

\bigskip

\textit{Lines 165 - 175: How second thresholds (CC values vs stations numbers) were chosen for each seismic station? If it is done manually, please provide a list of the threshold as the supplementary table. In addition, how many events did this selection step remove from the catalog? (A figure comparing before and after the selection step will be useful.)}

\bigskip

The choice of the threshold is explained in more detail later in the text, when we explain how we cleaned the longer catalog (2004-2011). The main idea is that if an LFE is present both in the 2007-2009 FAME catalog and in the 2004-2011 permanent networks catalog, then it is unlikely to be a false detection. We assumed that all LFEs present in both catalogs are true detections. The LFEs recorded during the period 2007-2009 that are present in only one catalog are then assumed to be false detections. Our goal is to maximize the number of true detections in the filtered catalogs. For the FAME catalog, we then chose a threshold such that at least 50 \% of the LFE detections kept in the FAME catalog after filtering with the threshold, are true detections, that is they are also in the networks catalog. For the networks catalog, we chose a threshold such that at least 50 \% of the LFE detections kept in the networks catalog after filtering with the threshold (and occurring between 2007 and 2009), are true detections, that i that are also in the FAME catalog. There are thus two thresholds per family. The filtering is done such that the product of the cross-correlation for a given LFE by the number of channels recording at the time when the LFE occurred is higher than the threshold. The thresholds chosen for the FAME and the networks catalog are then different because the stations and the quality of the templates are different for both catalogs. For the period 2004-2007 and 2009-2011, we used the same threshold as determined for the period 2007-2009 for the networks catalog. We added in a supplement a table with the values of the thresholds. \\

Our filtering method kept 37 \% of the LFEs for the networks catalog and 16 \% of the LFEs for the FAME catalog. We have added in the supplements figures of the catalogs without filtering the LFEs.

@@

\bigskip

\textit{Line 306: Which fault plane did authors assume to calculate tidal stress?}

\bigskip

The fault plane is the plate boundary model of McCrory et al. (2012): McCrory, P. A., Blair, J. L., Waldhauser, F., Oppenheimer, D. H. (2012) Juan de Fuca slab geometry and its relation to Wadati-Benioff zone seismicity. 
Journal of Geophysical Research: Solid Earth, 2012-09, Vol.117 (B9).

### 2022-01-26 paper/agujournaltemplate_highlighted.tex
Include revisions

Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes. They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface. \textbf{LFEs tend to happen in bursts, with dozen of earthquakes occurring within a few days, followed by weeks or months of quiet}. In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011. As in northern Cascadia, the \textbf{LFE families located at greater depth are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth. Earth tides have also an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary}.

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0.5cm 7cm 1.5cm 7cm},clip]{figures/map_LFEs.eps}
\caption{Map showing the location of the LFE families (black dots) and the seismic stations used in this study. Red triangles are the stations from the FAME experiment, green triangles are one-component permanent stations, blue triangles are three components permanent stations. Red stars are moderate ($M > 5$) nearby earthquakes. \textbf{Contour lines are the depth contours of the plate boundary model from ~\citeA{MCC_2006}. The cross section shows the depth of the LFE families. The line corresponds to the plate boundary model from ~\citeA{MCC_2006} at latitude 41N.}}
\label{pngfiguresample}
\end{figure}

@@

In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}. We want to verify whether we can see an increase of LFE activity for the downdip LFE families compared to the updip LFE families. Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other. We first look at three families aligned at latitude about 40.4N (group B, triangles in Figure 1) and show the number of LFEs per day in the left column of Figure 8. We then look at five families aligned at latitude about 40.7N (group C, diamonds in Figure 1) and show the number of LFEs per day in the middle column of Figure 8. Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8. For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}. It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected. To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor. We clearly see that the \textbf{average time between} decreases with the down dip distance. The southernmost family A is also added in Figure 9, but does not fit the general trend.\\

>>>>

Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes. They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface. \textbf{LFEs tend to happen in bursts, with dozen of earthquakes occurring within a few days, followed by weeks or months of quiet}. In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011. As in northern Cascadia, the \textbf{LFE families located at greater depth are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth. Earth tides also have an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary}.

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0.5cm 7cm 1.5cm 7cm},clip]{figures/map_LFEs.eps}
\caption{Map showing the location of the LFE families (black dots) and the seismic stations used in this study. Red triangles are the stations from the FAME experiment, green triangles are one-component permanent stations, blue triangles are three components permanent stations. Red stars are moderate ($M > 5$) nearby earthquakes. \textbf{Contour lines are the depth contours of the plate boundary model from ~\citeA{MCC_2006}. MF indicates the Maacama Fault. The cross section shows the depth of the LFE families. The line corresponds to the plate boundary model from ~\citeA{MCC_2006} at latitude 41N.}}
\label{pngfiguresample}
\end{figure}

@@

In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}. We want to verify whether we can see an increase of LFE activity for the downdip LFE families compared to the updip LFE families. Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other. We first look at three families aligned at latitude about 40.4N (group B, triangles in Figure 1) and show the number of LFEs per day in the left column of Figure 8. We then look at five families aligned at latitude about 40.7N (group C, diamonds in Figure 1) and show the number of LFEs per day in the middle column of Figure 8. Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8. For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}. It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected. To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor. \textbf{We defined an LFE event as at least five LFEs recorded during a given day. If two events are separated by less than five days, we assume that this is a single event.} We clearly see that the \textbf{average time between} decreases with the down dip distance. The southernmost family A is also added in Figure 9, but does not fit the general trend.\\

### 2022-01-26 paper/supplement.tex
Include revisions

\title{Supplementary Material}
\date{}
\maketitle

\begin{table}
\caption{Temporary stations used for the 2007-2009 catalog}
\centering
\begin{tabular}{c c c c c c c c c}
\hline
Station & Network & Channels & Location & Data center & Latitude & Longitude & Begin time & End time \\
\hline
B039 & PB & EH1,EH2,EHZ & -- & IRIS & 41.4667 & -122.4847 & 2007-10-15 & 3000-01-01 \\
KCPB & NC & HHE,HHN,HHZ & -- & NCEDC & 39.6863 & -123.5824 & 2002-10-17 & 3000-01-01 \\
KHBB & NC & HHE,HHN,HHZ & -- & NCEDC & 40.6599 & -123.2197 & 2003-09-11 & 3000-01-01 \\
KRMB & NC & HHE,HHN,HHZ & -- & NCEDC & 41.5230 & -123.9080 & 2001-06-16 & 3000-01-01 \\
KSXB & NC & HHE,HHN,HHZ & -- & NCEDC & 41.8304 & -123.8769 & 2001-07-13 & 3000-01-01 \\
ME01 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.7752 & -123.4034 & 2007-07-31 & 2009-06-12 \\
ME02 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.6898 & -122.3372 & 2007-07-22 & 2009-05-20 \\
ME03 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.702 & -123.881 & 2007-09-27 & 2009-06-13 \\
ME04 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.355 & -123.514 & 2007-07-23 & 2009-06-12 \\
ME08 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.222 & -123.305 & 2007-07-22 & 2009-06-03 \\
ME09 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.086 & -122.726 & 2007-07-21 & 2009-05-14 \\
ME10 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.9591 & -122.4619 & 2007-10-31 & 2009-06-12 \\
ME12 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.104 & -122.498 & 2007-07-20 & 2009-06-12 \\
ME13 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.764 & -122.918 & 2007-07-22 & 2009-06-12 \\
ME16 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.577 &  -122.087 & 2007-07-20 & 2008-10-14 \\
ME24 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.359 & -122.047 & 2007-07-19 & 2009-05-15 \\
ME26 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.157 & -122.099 & 2007-07-26 & 2009-02-17 \\
ME27 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.453 & -123.155 & 2008-01-01 & 2009-06-13 \\
ME28 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.327 & -122.471 & 2007-07-20 & 2009-05-14 \\
ME29 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.142 & -123.1408 & 2007-09-21 & 2009-06-13 \\
ME30 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.843 & -123.565 & 2007-07-24 & 2009-06-22 \\
ME42 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.7145 & -123.273 & 2007-07-15 & 2009-06-16 \\
ME43 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.5703 & -123.175 & 2007-09-16 & 2009-06-16 \\
ME44 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.4928 & -123.187 & 2007-09-16 & 2009-06-15 \\
ME45 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.4666 & -122.9595 & 2007-09-12 & 2009-06-09 \\
ME46 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.196 & -122.968 & 2007-09-25 & 2009-06-11 \\
ME47 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.1124 & -122.8106 & 2007-09-25 & 2008-09-17 \\
ME49 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.8633 & -123.7194 & 2007-09-25 & 2009-06-08 \\
ME52 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.3228 & -123.2191 & 2008-02-21 & 2009-07-08 \\
ME54 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.0132 & -123.3779 & 2007-09-24 & 2009-03-03 \\
ME57 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.9118 & -122.5676 & 2007-10-24 & 2009-06-11 \\
WDC & BK & BHE,BHN,BHZ & -- & NCEDC & 40.5799 & -122.5411 &1992-09-17 & 2011-05-06 \\
YBH &  BK & BHE,BHN,BHZ & -- & NCEDC & 41.7320 & -122.7104 & 1993-07-24 & 2011-06-03 \\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{Permanent stations used for the 2004-2011 catalog}

@@

>>>>

\title{An eight-year-long low-frequency earthquake catalog for Southern Cascadia}

\authors{Ariane Ducellier\affil{1}, Kenneth C. Creager\affil{1}}

\affiliation{1}{University of Washington}

\correspondingauthor{Ariane Ducellier}{ducela@uw.edu}

\begin{figure}[hbt!]
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/unfiltered_FAME.eps}
\caption{Same as Figure 3 from the main text, but without filtering the LFEs. They are many false detections at the beginning and the end of the catalog because the FAME stations were not yet installed / already removed.}
\label{pngfiguresample}
\end{figure}

\begin{figure}[hbt!]
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/unfiltered_perm.eps}
\caption{Same as Figure 6 from the main text, but without filtering the LFEs.}
\label{pngfiguresample}
\end{figure}

\begin{figure}[hbt!]
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/timeline_FAME.eps}
\caption{Evolution of the number of channels available for the computation of the 2007-2009 catalog using the temporary FAME stations.}
\label{pngfiguresample}
\end{figure}

\begin{figure}[hbt!]
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/timeline_perm.eps}
\caption{Evolution of the number of channels available for the computation of the 2004-2011 catalog using the permanent stations.}
\label{pngfiguresample}
\end{figure}

\newpage

\begin{table}[hbt!]
\caption{Temporary stations used for the 2007-2009 catalog. The data centers providing the seismic waveforms are the Incorporated Research Institutions for Seismology (IRIS) (Alan Levander, 2007), and the Northern California Earthquake Data Center (NCEDC), doi:10.7932/NCEDC.}
\centering
\footnotesize
\begin{tabular}{c c c c c c c c c}
\hline
Station & Network & Channels & Location & Data center & Latitude & Longitude & Begin time & End time \\
\hline
B039 & PB & EH1,EH2,EHZ & -- & IRIS & 41.4667 & -122.4847 & 2007-10-15 & 3000-01-01 \\
KCPB & NC & HHE,HHN,HHZ & -- & NCEDC & 39.6863 & -123.5824 & 2002-10-17 & 3000-01-01 \\
KHBB & NC & HHE,HHN,HHZ & -- & NCEDC & 40.6599 & -123.2197 & 2003-09-11 & 3000-01-01 \\
KRMB & NC & HHE,HHN,HHZ & -- & NCEDC & 41.5230 & -123.9080 & 2001-06-16 & 3000-01-01 \\
KSXB & NC & HHE,HHN,HHZ & -- & NCEDC & 41.8304 & -123.8769 & 2001-07-13 & 3000-01-01 \\
ME01 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.7752 & -123.4034 & 2007-07-31 & 2009-06-12 \\
ME02 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.6898 & -122.3372 & 2007-07-22 & 2009-05-20 \\
ME03 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.702 & -123.881 & 2007-09-27 & 2009-06-13 \\
ME04 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.355 & -123.514 & 2007-07-23 & 2009-06-12 \\
ME08 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.222 & -123.305 & 2007-07-22 & 2009-06-03 \\
ME09 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.086 & -122.726 & 2007-07-21 & 2009-05-14 \\
ME10 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.9591 & -122.4619 & 2007-10-31 & 2009-06-12 \\
ME12 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.104 & -122.498 & 2007-07-20 & 2009-06-12 \\
ME13 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.764 & -122.918 & 2007-07-22 & 2009-06-12 \\
ME16 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.577 &  -122.087 & 2007-07-20 & 2008-10-14 \\
ME24 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.359 & -122.047 & 2007-07-19 & 2009-05-15 \\
ME26 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.157 & -122.099 & 2007-07-26 & 2009-02-17 \\
ME27 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.453 & -123.155 & 2008-01-01 & 2009-06-13 \\
ME28 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.327 & -122.471 & 2007-07-20 & 2009-05-14 \\
ME29 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.142 & -123.1408 & 2007-09-21 & 2009-06-13 \\
ME30 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.843 & -123.565 & 2007-07-24 & 2009-06-22 \\
ME42 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.7145 & -123.273 & 2007-07-15 & 2009-06-16 \\
ME43 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.5703 & -123.175 & 2007-09-16 & 2009-06-16 \\
ME44 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.4928 & -123.187 & 2007-09-16 & 2009-06-15 \\
ME45 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.4666 & -122.9595 & 2007-09-12 & 2009-06-09 \\
ME46 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.196 & -122.968 & 2007-09-25 & 2009-06-11 \\
ME47 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.1124 & -122.8106 & 2007-09-25 & 2008-09-17 \\
ME49 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.8633 & -123.7194 & 2007-09-25 & 2009-06-08 \\
ME52 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.3228 & -123.2191 & 2008-02-21 & 2009-07-08 \\
ME54 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.0132 & -123.3779 & 2007-09-24 & 2009-03-03 \\
ME57 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.9118 & -122.5676 & 2007-10-24 & 2009-06-11 \\
WDC & BK & BHE,BHN,BHZ & -- & NCEDC & 40.5799 & -122.5411 &1992-09-17 & 2011-05-06 \\
YBH &  BK & BHE,BHN,BHZ & -- & NCEDC & 41.7320 & -122.7104 & 1993-07-24 & 2011-06-03 \\
\hline
\end{tabular}
\end{table}

\newpage

\begin{table}[hbt!]
\caption{Permanent stations used for the 2004-2011 catalog. The data centers providing the seismic waveforms are the Incorporated Research Institutions for Seismology (IRIS) (Alan Levander, 2007), and the Northern California Earthquake Data Center (NCEDC), doi:10.7932/NCEDC.}

@@

\newpage

\begin{table}[hbt!]
\caption{Thresholds used to clean the catalogs. An LFE is kept in the catalog if its cross-correlation value multiplied by the number of channels recording when it was detected is higher than the threshold. The threshold is missing for the families for which there were not enough permanent stations with good templates to obtain reliable LFE detections.}
\centering
\scriptsize
\begin{tabular}{c c c}
\hline
Family & Threshold 2007-2009 & Threshold 2004-2011 \\
\hline
080401.05.050 & 1.4 & 1.9 \\
080405.11.042 & 2.0 & 1.6 \\
080408.08.007 & 1.7 & 1.5 \\
080408.15.023 & 2.0 & 1.3 \\
080408.08.029 & 2.3 & 1.4 \\
080408.16.026 & 1.8 & 1.4 \\
080410.01.050 & 3.5 & 1.3 \\
080410.09.032 & 3.9 & 1.4 \\
080410.12.039 & 1.9 & 1.3 \\
080410.12.040 & 5.4 & 2.3 \\
080411.04.013 & 3.4 & 1.5 \\
080411.04.023 & 3.6 & 1.5 \\
080410.13.055 & 1.9 & 1.3 \\
080412.03.029 & 2.2 & 1.0 \\
080412.11.038 & 2.2 & 1.3 \\
080412.22.047 & 3.2 & 1.5 \\
080413.13.026 & 2.2 & 1.3 \\
080412.22.040 & 3.5 & 1.6 \\
080413.07.015 & 2.0 & 1.6 \\
080413.07.023 & 1.8 & 1.4 \\
080413.16.058 & 2.2 & 0.1 \\
080413.18.013 & 2.6 & 1.2 \\
080413.20.036 & 2.1 & 1.1 \\
080414.12.016 & 2.0 & 1.2 \\
080414.12.020 & 1.5 & 1.2 \\
080414.10.058 & 1.8 & 1.2 \\
080414.18.003 & NA & NA \\
080415.11.006 & 4.6 & 1.6 \\
080415.11.008 & 3.0 & 1.8 \\
080415.24.028 & 2.5 & 1.7 \\
080416.15.003 & 2.8 & 1.7 \\
080418.03.001 & 5.0 & 1.5 \\
080415.19.030 & 2.9 & 1.9 \\
080419.24.054 & 3.4 & 2.2 \\
080416.13.033 & 3.9 & 2.0 \\
080417.15.043 & 3.3 & 1.7 \\
080418.02.049 & 3.7 & 1.6 \\
080419.04.046 & 3.5 & 1.5 \\
080420.01.019 & 2.3 & 1.6 \\
080420.04.009 & 2.2 & 1.4 \\
080420.05.032 & 3.0 & 1.8 \\
080420.08.042 & 1.8 & 1.5 \\
080421.14.048 & 2.1 & 1.6 \\
080421.15.050 & 1.9 & 1.5 \\
080421.16.053 & 3.0 & 1.4 \\
080421.16.054 & 2.3 & 1.4 \\
080421.17.056 & 2.1 & 1.3 \\
080421.23.033 & 2.7 & 1.4 \\
080422.13.003 & 3.2 & 1.7 \\
080422.12.039 & 1.7 & 1.1 \\
080422.13.043 & 2.7 & 1.6 \\
080422.15.030 & 2.0 & 1.5 \\
080424.04.058 & 3.3 & 1.8 \\
080424.05.060 & 2.2 & 1.7 \\
080426.05.008 & 1.8 & 1.6 \\
080426.06.027 & 2.1 & 1.8 \\
080426.20.030 & 1.5 & 1.7 \\
080427.04.052 & 2.5 & 1.5 \\
080427.13.036 & 2.1 & 1.5 \\
080427.20.043 & 2.5 & 2.0 \\
080429.15.005 & NA & NA \\
080326.07.004 & NA & NA \\
080326.07.048 & NA & NA \\
080326.08.015 & 2.7 & 1.0 \\
080326.09.007 & NA & NA \\
080328.09.029 & NA & NA \\
\hline
\end{tabular}
\end{table}
